\papertitle

### 2017-03-30 article-icmc2017.tex
work

\section{Applied example: generative music}

\section{Conclusion}
Throughout this paper, the effects of adding macro-temporal semantics to dataflows were studied. 
The first step is to introduce an environment that allows execution of a program to continue if not all the nodes of a dataflow are currently being executed.
Then, we study the new possibilities offered by the presence of the environment by the different ways to interpret the absence of execution of a node.
This includes matching nodes together through pattern matching, and distinct policies of execution that can take into account the evolution of the program in time.

>>>>

\section{Applied example: generative music}
We present here an example that leverages patches built with Pure Data\cite{puckette1996pure}.
\begin{figure}[h]
	\centering
	\begin{subfigure}{0.21\textwidth}
		\includegraphics[scale=0.5]{images/pd-1.png}
		\caption{$f_1$: generates a random note on each bang}
	\end{subfigure}
\begin{subfigure}{0.21\textwidth}
	\includegraphics[scale=0.5]{images/pd-2.png}
	\caption{$f_2$: generates another random note on each bang}
\end{subfigure}

\begin{subfigure}{0.21\textwidth}
	\includegraphics[scale=0.5]{images/pd-3.png}
	\caption{$f_3$: synthesizes a note, sets the volume}
\end{subfigure}
\begin{subfigure}{0.21\textwidth}
	\includegraphics[scale=0.5]{images/pd-4.png}
	\caption{$f_4$: applies an high-pass filter}
\end{subfigure}
\begin{subfigure}{0.21\textwidth}
\includegraphics[scale=0.5]{images/pd-5.png}
\caption{$f_5$: applies a low-pass filter}
\end{subfigure}
\caption{The functions we use in our example, as defined in PureData.}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.7]{images/nodes.eps}

	\caption{The relationships between instances of $f_{1,..5}$ in the program}
\end{figure}

\begin{figure}
	\begin{tikzpicture}
	\input{scores/score2.tex}
	\end{tikzpicture}
	\caption{}
\end{figure}
\section{Conclusion}
Throughout this paper, the effects of adding macro-temporal semantics to dataflows were studied. 
The first step is to introduce an environment that allows execution of a program to continue if not all the nodes of a dataflow are currently being executed.
Then, we study the new possibilities offered by the presence of the environment by the different ways to interpret the absence of execution of a node.
This includes matching nodes together through pattern matching, and distinct policies of execution that can take into account the evolution of the program in time.
